---
title: "Homwework 6"
author: "Shubham Bhargava"
date: "2024-03-05"
output: github_document
---

```{r}
library(readxl)
News_Website_Dataset <- read_excel("News Website Dataset.xlsx")
#View(News_Website_Dataset)

# correlation  and coefficient B/W Total_revenue and Total Sessions
correlation_coefficient2 <- cor(News_Website_Dataset$Total_revenue, News_Website_Dataset$Total_Sessions)
print(correlation_coefficient2)

plot(News_Website_Dataset$Total_Sessions, News_Website_Dataset$Total_revenue,
     xlab = "Total Sessions", ylab = "Total Revenue",
     main = "Scatter Plot of Total Revenue vs. Total Sessions")

abline(lm(News_Website_Dataset$Total_revenue ~ News_Website_Dataset$Total_Sessions), col = "green")

```
```{r}

correlation_coefficient <- cor(News_Website_Dataset$Total_revenue, News_Website_Dataset$Avg_Session_Duration)

plot(News_Website_Dataset$Avg_Session_Duration, News_Website_Dataset$Total_revenue,
     xlab = "Average Session Duration", ylab = "Total Revenue",
     main = "Scatter Plot of Total Revenue vs. Avg Session Duration")

abline(lm(News_Website_Dataset$Total_revenue ~ News_Website_Dataset$Avg_Session_Duration), col = "purple")

print(paste("Correlation Coefficient between Total Revenue and Avg Session Duration:", correlation_coefficient))

```

### Assignment 6

<h4>Factor Analysis</h4>

<p><b>1. Decide how many Factors are ideal for your dataset</b></p>
<p>Parallel analysis suggests that the number of factors =  1  and the number of components =  1</p>

<p><b>2. Explain the output for your factor model</b></p>
<p><b>Standardized Loadings</b></p>
<p>Avg_Session_Duration has low loadings on all factors, with the highest loading on MR3 (0.32).</p>
<p>Total_Sessions has the highest loading on MR2 (0.34).</p>
<p>Total_revenue and Conversion_Rate both have the highest loadings on MR1 (0.48 and 0.50, respectively).</p>

<p><b>SS Loadings</b></p>
<p>MR1 explains 12% of the total variance., 
MR2 explains 4% of the total variance., 
MR3 explains 3% of the total variance.</p>

<p>MR1 might be related to conversion rate and potentially session duration (positive loadings).</p>
<p>MR2 is positively associated with the total number of sessions.</p>
<p>MR3 has weaker and mixed relationships with the variables.</p>

<p>we can conclude that a 3-factor solution adequately explains the structure of the data. Each factor captures a unique aspect of the underlying structure, with Total_revenue and Conversion_Rate loading primarily on MR1, Total_Sessions on MR2, and Avg_Session_Duration on MR3.</p>

<p><b> 3&4 Show the columns that go into each factor and Perform some visualizations using the factors</b></p>
<p>we can see the below code to answer 3&4.
```{r}
library(psych)
library(readxl)
data <- read_excel("News Website Dataset.xlsx")
data_num <- data[, c("Avg_Session_Duration", "Total_Sessions", "Total_revenue","Conversion_Rate")]
factor_model <- fa(data_num, nfactors = 3, rotate = "varimax")

fa.parallel(data_num[-1])
print(factor_model)

factor_loadings <- factor_model$loadings
print(factor_loadings)

#some visualizations
fa.plot(factor_model)      # See Correlations within Factors
fa.diagram(factor_model)   # Visualize the relationship
```